Performance of two different ontological and data access methods

### 2014-07-11 cold2014/magnus.tex
fixing the final figure
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@750 43ef1190-90fd-4dd7-a769-d0121f02b80e
remove too big to show
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@753 43ef1190-90fd-4dd7-a769-d0121f02b80e
mention mercedes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@754 43ef1190-90fd-4dd7-a769-d0121f02b80e

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself important, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using Semantic Web technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

@@

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  
With 10 factors the amount of
runs were $2^{10}$, which made the planning matrix too big to show here. 
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets.

@@

\begin{wraptable}{l}{0.25\textwidth}
%\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
      O & 58.17 \\ \hline
      E:FC & 45.69 \\ \hline
      O:E:FC & 45.55\\ \hline
      FC & 38.61\\ \hline
      O:FC & 38.56\\ \hline
      O:E & 35.40\\ \hline
      E & 35.38\\ \hline
      O:T & 33.12\\ \hline
      T & 33.12\\ \hline
      O:T:E:FC & 29.31\\ \hline
      T:E:FC & 29.30\\ \hline
      O:T:FC & 28.24\\ \hline
      T:FC & 28.23\\ \hline
      O:T:E & 25.31\\ \hline
      T:E & 25.30\\ \hline
    \end{tabular}
\caption{The top fifteen significant absolute effects of the ten factor graph}\label{10factorEffect}
%      \vspace{-25pt}
\end{wraptable}

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{bibliography,science}

>>>>

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself important, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using Semantic Web technologies. Volkswagen had
their data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their Mercedes A- and B-class cars.  The Daimler data used
a custom XML-based format, so we lifted the data using a
\textit{Python} script into the ontologies developed by Martin Hepp
and Volkswagen.

@@

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  
With 10 factors, we have $2^{10}$, which is quite large for a full
factorial experiment.
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets. % TODO: more on this.

@@

\begin{wraptable}{l}{0.25\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
      O & 58.17 \\ \hline
      E:FC & 45.69 \\ \hline
      O:E:FC & 45.55\\ \hline
      FC & 38.61\\ \hline
      O:FC & 38.56\\ \hline
      O:E & 35.40\\ \hline
      E & 35.38\\ \hline
      O:T & 33.12\\ \hline
      T & 33.12\\ \hline
      O:T:E:FC & 29.31\\ \hline
      T:E:FC & 29.30\\ \hline
      O:T:FC & 28.24\\ \hline
      T:FC & 28.23\\ \hline
      O:T:E & 25.31\\ \hline
      T:E & 25.30\\ \hline
    \end{tabular}
\caption{The top fifteen significant absolute effects of the ten factor graph}\label{10factorEffect}
      \vspace{-75pt}
\end{wraptable}

@@

%\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
%\bibliography{bibliography,science}
\input{magnus.bbl}
